---
title: "STA138Project"
author: "Haolin Li"
date: "3/18/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Problem 1: Low birth rate or not
```{r}
library("readxl")
baby = read_excel("~/Desktop/Statistics/STA138/baby.xls")
```


```{r}
second_baby = glm(birth~age+weight+smoke+pre+hyp+visits+age*weight+weight*hyp+weight*pre, family = 'binomial', data = baby)
summary(second_baby)

```


```{r}
first_baby = glm(birth~age+weight+smoke+pre+hyp+visits, family = 'binomial', data = baby)

anova(first_baby,second_baby, test = "Chisq")

```
#H0: beta7 = beat8 = beta9 = 0, HA = at least one of beta7, beta8 and beta9 is not zero.
#G^2 is 0.19127 and p-value of 0.979 is larger than 0.05. therefore we cannot reject H0. 
# Conclusion: interaction terms should not be added to the model

```{r}
step(first_baby)
```
# Backward function suggests drop (visit)(X6)
```{r}
reduced_baby = glm(birth~age+weight+smoke+pre+hyp, family = 'binomial', data = baby)
anova(reduced_baby,first_baby, test = "Chisq")
```
# H0: beta6 = 0, HA: beta6 not equal 0
# G^2 = 0.032333 p-value is 0.8573
# p-value is larger than 0.05, cannot reject H0
# Conclusion: we may drop X6 (Vistis is not significant)

```{r}
summary(reduced_baby)
```
# Smoke could be dropped

```{r}
reduced_baby = glm(birth~age+weight+smoke+pre+hyp+visits, family = 'binomial', data = baby)
check_baby = glm(birth~age+weight+pre+hyp, family = 'binomial', data = baby)
anova(check_baby,reduced_baby, test = "Chisq")
```
# H0: beta3 = 0, HA: beta3 not equal 0
# G^2 = 2.2026 p-value is 0.1378
# p-value is larger than 0.05, cannot reject H0
# Conclusion: we may drop X3 (smoke is not significant)

```{r}
summary(check_baby)
check_baby = glm(birth~age+weight+pre+hyp, family = 'binomial', data = baby)
final_baby = glm(birth~weight+pre+hyp, family = 'binomial', data = baby)
anova(final_baby,check_baby, test = "Chisq")
```
# Further Investigation:
# H0: beta1 = 0, HA: beta1 not equal 0
# G^2 = 3.0196 p-value is 0.08227
# p-value is smaller than 0.1, reject H0
# Here significance level is 0.01. 
# Conclusion: we may not drop X1 (age is significant)

```{r}
summary(check_baby)

```

#Problem 2
```{r}
chem = read_excel("~/Desktop/Statistics/STA138/ischemic.xlsx")
```
# Use Poisson because want to model its mean.

```{r}
second_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration+gender*cost+gender*age+gender*inter+gender*drugs+gender*complications+gender*comorbidities+gender*duration, family = poisson(), data = chem)
summary(second_chem)

```
# Consider dropping interaction terms except gender*complications
```{r}
first_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration, family = poisson(), data = chem)

third_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration+gender*cost+gender*age+gender*inter+gender*drugs+gender*comorbidities+gender*duration, family = poisson(), data = chem)

anova(first_chem,third_chem, test = "Chisq")


```
# Drop all interaction except gender*complications

```{r}
check1_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration, family = poisson(), data = chem)

check2_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration+gender*complications, family = poisson(), data = chem)

anova(check1_chem,check2_chem, test = "Chisq")

```
# Keep gender*complication

```{r}
step(check2_chem)
```
#Suggests drop comorbidities

```{r}
fourth_chem = glm(visits~cost+age+gender+inter+drugs+complications+duration+gender*complications, family = poisson(), data = chem)

anova(fourth_chem,check2_chem, test = "Chisq")
```
# Drop comorbidities
```{r}

final_chem = glm(visits~cost+age+gender+inter+drugs+complications+duration+gender*complications, family = poisson(), data = chem)

anova(final_chem,fourth_chem, test = "Chisq")
```
#Further Investigation 
#Drop duration if significance level is 0.01
#Drop age if significance level is 0.001
```{r}
summary(fourth_chem)
```

```{r}
res_chem = residuals(fourth_chem, type = "deviance")
plot(res_chem, main = "Problem 2 Untransformed: Deviance Residuals Plot", xlab = "Observations", ylab = "Residual" )

```

# Transformation of Variables
```{r}
trans_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration+sqrt(cost)+sqrt(age)+sqrt(inter)+sqrt(drugs)+sqrt(complications)+sqrt(comorbidities)+sqrt(duration)+gender*sqrt(cost)+gender*sqrt(age)+gender*sqrt(inter)+gender*sqrt(drugs)+gender*sqrt(complications)+gender*sqrt(comorbidities)+gender*sqrt(duration), family = poisson(), data = chem)
summary(trans_chem)

```
# Drop all interaction terms except gender:sqrt(complications) 
```{r}
trans2_chem = glm(visits~cost+age+gender+inter+drugs+complications+comorbidities+duration+sqrt(cost)+sqrt(age)+sqrt(inter)+sqrt(drugs)+sqrt(complications)+sqrt(comorbidities)+sqrt(duration)+gender*sqrt(complications), family = poisson(), data = chem)

anova(trans2_chem,trans_chem, test = "Chisq")
```
# Dropped all interction terms except gender:sqrt(complications) 

```{r}
step(trans2_chem)
```
# Suggests drop cost,drugs,complications, comorbidities, sqrt(gender), sqrt(inter),sqrt(duration)
```{r}
trans3_chem = glm(formula = visits ~ age + gender + inter + duration + sqrt(cost) + sqrt(age) + sqrt(drugs) + sqrt(complications) + sqrt(comorbidities) +gender*sqrt(complications), family = poisson(), data = chem)

anova(trans3_chem,trans2_chem, test = "Chisq")

```
# Dropped Supported

```{r}
summary(trans3_chem)
```
# Should I Drop sqrt(comorbidities)?


```{r}
res_trans_chem = residuals(trans3_chem, type = "deviance")
plot(res_trans_chem, main = "Problem 2 Transformed: Deviance Residuals Plot", xlab = "Observations", ylab = "Residual" )

```


























